Title

### 2013-03-21 inc/gun/gun_design.tex
tweaks in gun section

These requirements lead to the fabrication of cathode/Wehnelt and anode pair based on the design of Togawa \textit{et al.} \cite{togawa_ceb6_2007} (pictured in \ref{fig:togawa-pic}).
A schematic of this design, overlayed by a Finite Element Model (FEM) simulation of the electic field, is shown in \ref{fig:gun-field}.
The schematic shows that the aperture concerns are easily satisfied.
From the field equipotentials, it is clear that this design has a consistently flat electric field for large displacements off the central axis.

\begin{figure}
  \centering
  \input{gunfield}
  \caption[Schematic of the employed Togawa-inspired custom cathode-anode pair]{
    Schematic of the employed Togawa-inspired cathode ($-V$) and anode (0V) pair.
    The emission source is inserted behind the cathode Wehnelt.
    Also shown are simulated equipotential lines generated by FEM modeling.
    The separation of the cathode and anode is adjustable to allow a greater range of input laser angles if needed. 
  }
  \label{fig:gun-field}
\end{figure}

Of course, as derived in Section \ref{sec:gun_model}, the change of electric field strength near the anode will cause some divergence of the electic field.
This field will cause a divergence of the beam.
Future work will include investigating the designs of Butler %TODO reference
which may be able to build in an intrinsic lensing to compensate for this effect.

%TODO comment on alignment
%TODO comment on high voltage
%TODO comment on EV parts etc

Re-alignment of cathode and anode is sometimes necessary to direct the emitted beam down the center axis of the column.
To facilitate this, the prototype column has the photocathode and Wehnelt mounted on the end of the high voltage feedthrough, which is in turn mounted on a two axis alignment mechanism.
Although this mechanism, called a ``port aligner,'' is typically used to couple two non-colinear vacuum ports, for use in this instrument it has been modified to be able to manually adjust the aligner during use.
In contrast to this flexibility, the anode is mounted to column using Kimball Physics's ``eV Parts'' mounting systems.
These strictly manufactured mounting hardwares ensure that the anode is properly aligned with the remainder of the microscope column.
Thus, by iteratively repositioning the input laser and then the gun alignment, the beam may be walked to pass as near as possible down the axis of the column.

>>>>

These requirements lead to the fabrication of cathode/Wehnelt and anode pair based on the design of Togawa \textit{et al.} \cite{togawa_ceb6_2007} (pictured in \ref{fig:togawa-pic}).
A schematic of this design, overlayed by a Finite Element Model (FEM) simulation of the electic field, is shown in \ref{fig:gun-field}.
The simulation was performed using \texttt{FreeFEM++}, a free finite element partial differential equation solver and meshing toolkit (\url{http://www.freefem.org/ff++/index.htm}).
The FEM simulation modeled the features of the anode and cathode, while emulating gap walls at infinity by placing a linear potential on gap edges at a large distance.
From the field equipotentials, it is clear that this design has a consistently flat electric field for large displacements off the central axis.
Since the shape of the field is scale independent, the schematic shows that the aperture width and laser acceptance concerns are easily satisfied for an appropriate choice of scale.

\begin{figure}
  \centering
  \input{gunfield}
  \caption[Schematic of the employed Togawa-inspired custom cathode-anode pair]{
    Schematic of the employed Togawa-inspired cathode ($-V$) and anode (0V, ground) pair.
    The emission source is inserted behind the cathode Wehnelt.
    The separation of the cathode and anode is adjustable to allow a greater range of input laser angles if needed. 
    Also shown are simulated equipotential lines generated by FEM modeling.
    The acceleration gap is modeled as having linear potential along an edge at a very large width. 
  }
  \label{fig:gun-field}
\end{figure}

As derived in Section \ref{sec:gun_model}, the change of electric field strength near the anode will cause some divergence of the electic field.
This field will cause a divergence of the beam.
Future work will include investigating the designs of Butler %TODO reference
which may be able to build in an intrinsic lensing to compensate for this effect.

A gross realignment of the cathode and anode is sometimes necessary to direct the emitted beam down the center axis of the column.
To facilitate this, the prototype column has the photocathode and Wehnelt mounted on the end of the high voltage feedthrough, which is in turn mounted on a two axis alignment mechanism.
Although this mechanism, called a ``port aligner,'' is typically used to couple two non-colinear vacuum ports, for use in this instrument it has been modified to be able to manually adjust the aligner during use.
In contrast to this flexibility, the anode is mounted to column using Kimball Physics's ``eV Parts'' mounting systems.
These strictly manufactured mounting hardwares ensure that the anode is properly aligned with the remainder of the microscope column.
Thus, by iteratively repositioning the input laser and then the gun alignment, the beam may be walked to pass as near as possible down the axis of the column.
